Classless Java

### 2016-03-23 OOPSLA16/sections/Translation.tex
revise S4

Figure~\ref{figure:valid} and Figure~\ref{figure:ofmethod} present more details on the auxiliary
functions. 
The first two points of Figure~\ref{figure:valid}
defines function $\otherMethod$;
 This function generates unimplemented
 \Q@with-@ and fluent setters in the interface, where the 
return types has been refined.

To determine whether a method need to be generated,
we check if such \Q@with-@ or setter methods
require an implementation in $\C_0$, but not declared directly in $\C_0$.

The third point gives the definition
of $\valid$:
It is valid to annotate an interface if 
%To generate the \Q@of@ method, it is necessary for $\weakAnn$ to explicitly check if
all abstract methods (that is, all those
requiring an implementation) are valid.
That is, we can categorize them in a pattern that we
know how to implement (right column):
it is either a field getter (first point),
a with method (second point) or a setter (third point).

@@

Figure~\ref{figure:ofmethod},
defines the $\ofMethod$  function, that generates the static method $\QM{of}$ as an
object factory.
It detects all the field methods of $\C_0$ and use them to synthesize
its arguments.
The return statement instantiate an anonymous class which
generates the needed getters, fluent setters and with-methods.

The right column first point collect the getter methods,
the second and third point generate implementations for with methods
if needed; similarly, the fourth and fifth point generate fluent setters if needed.

@@

To formally characterize the behavior of our annotation and the two levels of guarantees that we offer, we provide some notations and two theorems:
\begin{itemize}
\item We denote with $\C^{\II}$ and $m^\method$ the name of an interface and of a method.
\item An interface table
IT is OK if under such interface table, all interfaces are OK,
\marcoT{that is, well typed}.
\item Since interface tables are just represented as sequences of interfaces we write IT = $\II$ IT' to select a specific interface in a table.
\item IT contains an heir of $\C$ if there is an interface that extends it, or a \Q@new@ that instantiate it.
\end{itemize}

@@

Informally, the theorems mean that for a client program that
typechecks before the translation is applied, if the annotated type has
no subtypes and no objects of that type are created, then type safety
\marcoT{of the generated code}
is guaranteed after the successful translation.

>>>>

Figure~\ref{figure:valid} and Figure~\ref{figure:ofmethod} present more details on the auxiliary
functions. 
The first two points of Figure~\ref{figure:valid}
define function $\otherMethod$;
 This function generates unimplemented
 \Q@with-@ and fluent setters in the interface, where the 
return types has been refined.

To determine whether a method needs to be generated,
we check if such \Q@with-@ or setter methods
require an implementation in $\C_0$, but not declared directly in $\C_0$.

The third point gives the definition
of $\valid$:
it is valid to annotate an interface if 
%To generate the \Q@of@ method, it is necessary for $\weakAnn$ to explicitly check if
all abstract methods (that is, all those
requiring an implementation) are valid.
That is, we can categorize them in a pattern that we
know how to implement (right column):
it is either a field getter (first point),
a with method (second point) or a setter (third point).

@@

Figure~\ref{figure:ofmethod} 
defines the $\ofMethod$  function, that generates the static method $\QM{of}$ as an
object factory.
It detects all the field methods of $\C_0$ and use them to synthesize
its arguments.
The return statement instantiates an anonymous class which
generates the needed getters, fluent setters and with-methods.

The right column first point collects the getter methods,
the second and third point generate implementations for \texttt{with-} methods
if needed; similarly, the fourth and fifth point generate fluent setters if needed.

@@

To formally characterize the behavior of our annotation and the two levels of guarantees that we offer, we provide some notations and two theorems:
\begin{itemize}
\item We denote with $\C^{\II}$ and $m^\method$ the name of an interface and of a method.
\item An interface table
IT is OK if under such interface table, all interfaces are OK,
\marcoT{that is, well typed}.
\item Since interface tables are just represented as sequences of interfaces we write IT = $\II$ IT' to select a specific interface in a table.
\item IT contains an heir of $\C$ if there is an interface that extends it, or a \Q@new@ that instantiates it.
\end{itemize}

@@

Informally, the theorems mean that for a client program that
type-checks before the translation is applied, if the annotated type has
no subtypes and no objects of that type are created, then type safety
\marcoT{of the generated code}
is guaranteed after the successful translation.
